Guarded Recursion in Agda via Sized Types

### 2019-01-17 code-oneclock-paper/latex/Introduction.tex
WIP: intro

@@

To compare the strength of these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
This shows that guarded recursive type theory can be done via sized types.
More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
Simple types are interpreted via the usual presheaf semantics.

>>>>

Using techniques for representing ``type theory in type theory''
\cite{Chapman09,AltenkirchK16}, in Section \ref{sec:syntax} we present
an Agda formalization of the syntax of a simple type theory with
guarded recursion. This object language, that we call \GTT, is a variant of Atkey and
McBride's type system for productive coprogramming
\cite{atkey2013productive} in which the clock context can contain at
most one clock.

In Section \ref{sec:presheaf_sem}, we develop a denotational semantics
for \GTT\ using sized types. More precisely, we define a presheaf
model where the type formers of simply typed lambda calculus are
evaluated using the standard Kripke semantics. Typically the semantics
of type theories for guarded recursion is given in the topos of
trees or variations thereof \cite{BMSS-synthetic} \NV{Add citations here}.
In order to make clear the connections between guarded recursion and
sized types, we take the preorder of sizes as the indexing
category of our presheaves. This means that types and contexts of \GTT\ are
interpreted as antitone sized types.

@@

%% To compare the strength of these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
%% This shows that guarded recursive type theory can be done via sized types.
%% More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
%% Simple types are interpreted via the usual presheaf semantics.
